Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-02-28 paper/ms.tex

\subsection{Dark Matter Halo Number Density}
... We comment first on the intergrated dark matter halo surface
density as a function of mass for each one o the 210 sub-volumes in
the Bolshoi simulation. This will allows us to better understand the
expected trends for the LAEs preferred mass and the occupation
fraction. Figure \ref{fig:laes_dist} show these distributions.

The shadowed region in Figure \ref{fig:laes_dist} shows the surface
density values allowed by the observations. This figure tells us by
inspection which model parameters cannot reproduce the
observations. The regions where the DM surface density values are
below the observational constraint correspond to high masses. For a
model ${\mathcal M}$ with a minimum mass in this high mass range, the
observations present a surface density to high to be possible
achieved.

Conversely the regions where the halo surface density is higher than
the observational constraints correspond to models ${\mathcal M}$ with
a minimum mass below this threshold. Models with this minimum mass
hava a chance for successfuly reproducing observations if the
occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo
number density down to the observed value.

@@

... Figure presents the results for two mock fields for the same
model, the two have extreme values for the KS test.

Conversely here are different models where the KS test yield values of
$P\sim 1$. To illustrate the kind of success represented by these
models, we have selected these best ones in the case of the method
{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
distribution of the mock surveys, the smaller panel shows the
corresponding surface density distribution and the observational
constraint.

@@

\section{Conclusions}
In this letter we have presented new method to estimate preferred
mass for dark matter halos hosting Lyman Alpha Emitters at
$z=3.1$. The method is based on making an estimate of the cosmic
variance from different observed fields. Based on a Nbody simulation,
we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
host LAEs being compatible witht the cosmic variance constraints.

>>>>

\subsection{Dark Matter Halo Number Density}
We present first the results for  the intergrated dark matter halo surface
density as a function of halos mass for each one o the 210 sub-volumes in
the Bolshoi simulation. This result allowsus to better understand the
expected trends for the LAEs' preferred mass and the occupation
fraction. Figure \ref{fig:laes_dist} show these results. The continous lines
correspond to the subvolumes. The shadowed area indicates the surface
density values for LAEs allowed by the observations.

From this Figure we can read which models cannot reproduce the
observations. Regions in the plot where the halo surface density
values are below the observational constraint correspond to high
masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
$M_{\rm   min}$ located in that mass range, the surface density is too
low compared with observations.

Conversely, there are regions in the plot where the halo surface
density can be higher than the observational constraints correspond to
models ${\mathcal M}$ with a minimum mass below this threshold. Models
with this minimum mass hava a chance for successfuly reproducing
observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to
lower the halo number density down to the observed value.

@@

To illustrate this point, in Figure \ref{fig:mocks} we present the
results for two mock fields for the {\tt{Match}} method for a model
with the same parameters, but two extreme values for the KS test.

Conversely there are different models where the KS test yield values of
$P\sim 1$. To illustrate the kind of success represented by these
models, we have selected these best ones in the case of the method
{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
distribution of the mock surveys, the smaller panel shows the
corresponding surface density distribution and the observational
constraint.

@@

\section{Conclusions}
In this Letter we have constrained the preferred mass for dark matter
halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
method that matches the cosmic variance in the surface
density number of LAEs from differente observed fields. From this we
are able to constrain the mass range of dark matter halos hosting LAEs
to be in the range $<M_{\rm h}<$ and a corresponding occupation fraction
that escales as $f_{\rm occ} = M_{\rm min}$ with the minium halo mass
defining the halo mass range.

In this letter, this estimate is based on a large Nbody simulation
where we select a range a fraction of halos in a given mass range to
host LAEs. We explicitly construct mock observations to derive
statistics that can be compared against observations.

 The method is based on making an estimate of the cosmic
variance from different observed fields. Based on a Nbody simulation,
we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
host LAEs being compatible witht the cosmic variance constraints.
